\tool: Revisiting BadUSB with Type-C

### 2021-03-18 WOOT/Files/experiment.tex
🚧

\begin{table*}[t]
	\centering
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		\textbf{Category}  					& \textbf{Application} & \textbf{Leaked Sensitive Information}		& \textbf{Leaked Sensitive Information after Authentication} \\
		\hline
		Social \& Finance App 				& WeChat      & WeChat account, Asset status, chat history    		& \\
		\hline
		\multirow{3}{*}{Social App}			& QQ          & QQ account, interpersonal nexus, chat history   	& \\
											\cline{2-4}
							       			& Twitter     & Twitter account, interpersonal nexus            	& \\
											\cline{2-4}
							       			& Gmail       & Gmail account, Mail records                     	& \\
		\hline
		\multirow{3}{*}{Finance App}       	& Alipay      & Alipay account, Asset status         				& \\
											\cline{2-4}
											& ICBC        & ICBC account, password, Asset status  				& \\
											\cline{2-4}
											& Paypal      & Paypal account, bank accounts, Asset status     	& \\
		\hline
		\multirow{2}{*}{Tool}               & Chrome      & Sites visited                                   	& \\
											\cline{2-4}
		                					& Health      & Personal physical metrics      						& \\
		\hline
		\multirow{2}{*}{System}             & Settings - WiFi   & WiFi SSID                                	&  WiFi password \\
											\cline{2-4}
		                					& Settings - VPN    & VPN address, VPN account, VPN password      						& \\
		\hline
	\end{tabular}
	\linebreak
	\caption{Information Extraction via Manual Analysis.}
	\label{table:information_extracted}
\end{table*}

>>>>

\begin{table*}[t]
	\centering
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		\textbf{Category}  					& \textbf{Application} & \textbf{Leaked Sensitive Information}		& \textbf{Leaked Sensitive Information after Authentication} \\
		\hline
		Social \& Finance App 				& WeChat      & Account, Asset status, Chat History, Payment Code   & \\
		\hline
		\multirow{3}{*}{Social App}
											%& QQ          & Account, Interpersonal Nexus, Chat History   	& \\
											%\cline{2-4}
							       			& WhatsApp    & Account, Interpersonal Nexus, Chat History, Phone Number           	& \\
											\cline{2-4}
							       			& Facebook    & Account, Posts, Interpersonal Nexus, Contact Info                     	& \\
		\hline
		\multirow{3}{*}{Finance App}       	& Alipay      & Account, Asset status, Payment Code         				& \\
											\cline{2-4}
											& Cash App    & Email, Phone Number, Cash Balance			& \\
											\cline{2-4}
											& Paypal      & Account, PayPal Balance     				& \\
		\hline
		\multirow{1}{*}{Shopping App}		& Amazon Shopping  & Account, Orders, Shopping Cart         & \\
											%\cline{2-4}
		                					%& Taobao      & Personal physical metrics      						& \\
		\hline
		\multirow{2}{*}{Tool}               & Chrome      & Browsing History                                	& \\
											\cline{2-4}
		                					& Health      & Personal Physical Metrics      						& \\
		\hline
		\multirow{2}{*}{System}             & Contacts    &                                 	&  WiFi password \\
											\cline{2-4}
											& Settings - WiFi   & WiFi SSID                                	&  WiFi password \\
											\cline{2-4}
		                					& Settings - VPN    & VPN address, VPN account, VPN password      						& \\
		\hline
	\end{tabular}
	\linebreak
	\caption{Information Extraction.}
	\label{table:information_extracted}
\end{table*}
